### 2018-07-09 FrascatiPlot/Paper/NucleiB2.tex
chapter 4.2 first version completed

In figure~\ref{fig:CompareThermalAndCoalescence}, the data available data for (anti-)deuteorns, (anti)\hethree\ and \hthreelambda~\cite{Adam:2015yta} is compared to both coalescence and thermal model predictions. For the coalescence predictions, the radius parameterisation tuned to the data is used. The combined thermal model and blast-wave predictions are calculated as described in section~\ref{sec:thermal}. As a first observation, one sees that for deuterons and \hethree\ both approaches lead to similar predictions and give a reasonable description of the experimental data. However, both approaches show large differences for the \hthreelambda\ caused by the significantly larger size of  \hthreelambda\ with respect to \hethree. As a matter of fact, the only available data point so far shows a better agreement with the thermal+BW model than with the coalescence model. However, some authors argue that the difference to the coalescence model might be explained by a later formation through $\Lambda$s and deuterons~\cite{Zhang:2018euf}. In addition, the presence of an excited state with $J=3/2$ of the hyper-triton would significantly enhance the phase space for its production which is not considered here as there is no evidence for its existence~\cite{Mart:1996ay}. The determination of the exact potential enhancement factor is beyond the scope of this paper as it requires at least a rough knowledge of the wave-function, but a factor of two would be expected from counting the spin states.

@@

Figure~\ref{fig:CompareThermalAndCoalescence} also shows most importantly that the difference between the two approaches increases with decreasing source volume, thus underlining the need for additional and more precise data as a function of multiplicity and collision centrality in order to distinguish the two production scenarios. This behaviour also highlights the unique potential to constrain the wave-function of the particle under study at the moment of its production.

 - add an estimate for the hyper-triton in pp collisions

@@

In the following, we summarise our main conclusions:
\begin{enumerate}
	\item Thermal and coalescence models give similar predictions for the production of $A$=2 and $A$=3 (anti-)nuclei in heavy-ion collisions for a source volume that is constrained by experimental data on (anti-)deuteron production.
	\item Thermal and coalescence models give very different predictions for the production of hyper-tritons as a function of source volume in pp, p-Pb, and Pb-Pb collisions. In particular, the yield of hyper-tritons appears to be suppressed by a factor of about ???? in pp collisions with respect ot the production of \hethree.
\end{enumerate}

>>>>

In figure~\ref{fig:CompareThermalAndCoalescence}, the data available data for (anti-)deuteorns, (anti)\hethree\ and \hthreelambda~\cite{Adam:2015yta} is compared to both coalescence and thermal model predictions. For the coalescence predictions, the radius parameterisation tuned to the data is used. The combined thermal model and blast-wave predictions are calculated as described in section~\ref{sec:thermal}. As a first observation, one sees that for deuterons and \hethree\ both approaches lead to similar predictions and give a reasonable description of the experimental data. However, both approaches show large differences for the \hthreelambda\ caused by the significantly larger size of  \hthreelambda\ with respect to \hethree. As a matter of fact, the only available data point so far shows a better agreement with the thermal+BW model than with the coalescence model. However, some authors argue that the difference to the coalescence model might be explained by a later formation through $\Lambda$s and deuterons~\cite{Zhang:2018euf}. In addition, the presence of an excited state with $J=3/2$ of the hyper-triton would significantly enhance the phase space for its production which is not considered here as there is no evidence for its existence~\cite{Mart:1996ay}. The determination of the exact potential enhancement factor is beyond the scope of this paper as it requires at least a rough knowledge of the wave-function, but a factor of two would be expected from only counting the spin states.

@@

Figure~\ref{fig:CompareThermalAndCoalescence} also shows most importantly that the difference between the two approaches increases with decreasing source volume, thus underlining the need for additional and more precise data as a function of multiplicity and collision centrality in order to distinguish the two production scenarios. This behaviour also highlights the unique potential to constrain the wave-function of the particle under study at the moment of its production via precise measurements of the coalescence parameter as a function of the source volume. The curves presented here also explicitly allow for an estimate of the expected hyper-triton production in pp collisions. As can be seen, its production in pp collisions is expected to be suppressed by about two orders of magnitude with respect to that of \hethree, thus making this measurement a prime candidate for future experimental study.

@@

In the following, we summarise our main conclusions:
\begin{enumerate}
	\item Thermal and coalescence models give similar predictions for the production of $A$=2 and $A$=3 (anti-)nuclei in heavy-ion collisions for a source volume that is constrained by experimental data on (anti-)deuteron production.
	\item Thermal and coalescence models give very different predictions for the production of hyper-tritons as a function of source volume in pp, p-Pb, and Pb-Pb collisions. In particular, the yield of hyper-tritons appears to be suppressed by about two orders of magnitude in pp collisions with respect ot the production of \hethree.
\end{enumerate}
